% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{multirow}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Phone} 8291256765
\end{quote}
\end{minipage} &
\multirow{2}{*}{\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{Caleb Felix}
\end{quote}
\end{minipage}} & \begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{LinkedIn} linkedin.com/in/calebfelix
\end{quote}
\end{minipage} \\
\begin{minipage}[b]{\linewidth}\raggedright
\begin{quote}
\textbf{E-mail} calebfelix38@gmail.com
\end{quote}
\end{minipage} & & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Github} github.com/calebfelix
\end{minipage} \\
\midrule()
\endhead
\bottomrule()
\end{longtable}

\begin{quote}
A developer who is eager to learn and wants to apply his knowledge in
the real world. Works at a fast pace to meet tight deadlines. An
enthusiastic team player ready to contribute to the
company\textquotesingle s success.

\textbf{Education}
\end{quote}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Course}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Institute}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Year of Passing}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Percentage/CGPA}
\end{minipage} \\
\midrule()
\endhead
Bachelor of Engineering: IT & \emph{Xavier Institute of Engineering} &
2023 & 8.15 CGPA \\
H.S.C & \emph{Wilson College} & 2019 & 58.96\% \\
S.S.C & \emph{Ryan International} & 2017 & 70.8\% \\
\bottomrule()
\end{longtable}

\begin{quote}
\textbf{Technical Skills}

•Python\\
•HTML / CSS / JS\\
•Linux

\textbf{Internships}

\textbf{Web Developer}\emph{MyCryptoMart, Mumbai}
\textbar{}\textbf{2021-12 - 2022-05}\\
•Collaborated with the front-end team and created Back-end for the
MyCryptoMart website.

•Implemented API integration with OpenSeas platform\\
•Planned website development, converting mock-ups into usable web
presence with HTML, JavaScript, Express, EJS and JSON coding.

\textbf{Software Developer Intern}\emph{Trainity, virtual}
\textbar{}\textbf{2021-09 - 2021-11}•Developed several web applications
using Mongo dB, Express, Node.•Hosted Web Application to the internet.

•Developed an understanding of working of an API.

\textbf{Projects}

•\textbf{Music Catalogue Management System using Flask:} A web-based
music application where the user can store the music in an organized
manner. also took part in inter-college PRAGATI Project competition.
Flask, mysql\\
•\textbf{Paying Guest website:} A website where PG students may discover
suitable accommodation. Node, mongodb, express

\textbf{Certifications}

•Crash Course on Python by Google \textbar{} \textbf{2020-07}\\
•Using Python to Interact with the Operating System by Google \textbar{}
\textbf{2021-08}

\textbf{Areas of Interest}

•Cybersecurity\\
•Web Dev\\
•Artificial Intelligence

\textbf{Technical Paper Publications}

•``Zeco - The Cleanup Bot'' IJIRT (International Journal of Innovative
Research in Technology) \textbar{} \textbf{2023-05}\\
Paper ID: 159524 Volume 9, Issue 12\\
IOT-based final year project a vacuum cleaner bot that can be both
automatically operated as well as manually using Arduino uno
microcontroller and a BLDC motor to make it much more optimised than the
existing systems.
\end{quote}

\end{document}
